Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
more comments on figure 4
comment on figure 1

\newcommand{\ipt}{IPT\xspace}
\newcommand{\ipts}{IPTs\xspace}

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example.png}
\caption{Spatial and group organization provided by subject 1.}
\label{fig:xp2display}
\end{figure}

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/clusterAnalysis.png}
\caption{Cluster analysis of the similarity judgments. $j/I$ and $j/Pt$ compare the partition obtained using the similarity judgments clustered using a growing number of clusters versus respectively the instrument partition and the playing technique partition. Normalizing null partitions based NMI $nullI$ and $nullPt$ are used to obtain normalized measures: $nj/I$ and $nj/Pt$.
\vl{This line plot is very hard to understand.
The legend box occludes the data on the top-right corner.
It would be preferable to remove this legend box and label lines
by placing text upon them,
so that the plot would be legible to readers with color vision deficiencies.
Besides, the choice of line labels is cryptic, as it relies on abbreviations.
The NMI abbreviation should be expanded.
@figure}}
\label{fig:clusters}
\end{figure}

>>>>

\newcommand*{\eg}{e.g.\@\xspace}
\newcommand{\ipt}{IPT\xspace}
\newcommand{\ipts}{IPTs\xspace}

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example.png}
\caption{Spatial and group organization provided by subject 1.
\vl{It would be good to show the three stages of the human-computer interface:
random initialization,
geometric clustering on screen,
and color clustering.
Besides, the figure is not accessible to readers with
color vision deficiencies at the moment.
The color of the clusters should be reinforced with
geometrical information, \eg{} Voronoi cells.
@data @figure}}
\label{fig:xp2display}
\end{figure}

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/clusterAnalysis.png}
\caption{Cluster analysis of the similarity judgments. $j/I$ and $j/Pt$ compare the partition obtained using the similarity judgments clustered using a growing number of clusters versus respectively the instrument partition and the playing technique partition. Normalizing null partitions based NMI $nullI$ and $nullPt$ are used to obtain normalized measures: $nj/I$ and $nj/Pt$.
\vl{This line plot is very hard to understand.
The legend box occludes the data on the top-right corner.
It would be preferable to remove this legend box and label lines
by placing text upon them,
so that the plot would be legible to readers with color vision deficiencies.
Besides, the choice of line labels is cryptic, as it relies on abbreviations.
The distinction between I and Pt
can be illustrated by two complementary colors, \eg{} blue versus orange.
The distinction between j, nj, and null
can be illustrated by three distinct markers
(empty circle, filled triangle, asterisk),
associated with
three distinct line styles (solid, dashed, dotted).
The NMI abbreviation should be expanded.
@figure}}
\label{fig:clusters}
\end{figure}
